Filmchat

### 2017-06-15 paper/paper.tex
Updated paper

\chapter{Project Description}
\section{Vision}
Imagine the following scenario.You, and one or more friends, or maybe a romantic partner, are sitting int the sofa in front of the TV. You are having a movie night, but you are not quite sure what you should see. While you sit and discuss your likes, and dislikes, there is a microphone hidden in the corner. The listens to what you are saying, and it is sending it to an Interactive System. It understands, who is speaking, who is liking a movie, and who is not liking a movie. It also has, from earlier experience, knowledge of what you and maybe the ones you are with have seen, and liked. It also knows what you did not like.

@@

\chapter{Interactive System: Description}
There are two parts implemented in this system
The first part listens to a given channel on Slack, using the outgoing webhook.
\cite{SlackOutgoingSlack}
The second part uses Googles Speech API \cite{GoogleCloudPlatformSpeechPlatform} and listens to the microphone. It then tries to search for the terms in the recognized speech and if it finds a movie within it it posts it to the same Slack channel.

The thought of using both of these ways of integrating, was to be able to understand natural language surrounding how people talk and chat about movies, and then later on have the different parts use the same components.

The vision of the project, not the actual implementation sadly, aimed to follow the design guidelines give in the chapter about Social Natural User Interfaces \(NUI\) that Wigdor and Wixon talks about in ther Brave NUI World book. \cite{WigdorBraveWorld}

Some of the ones I believe fitting to Filmchat are:
\begin{itemize}
\item Create an experience that comes alive with several users, so that the experience
is more fun or efficient when many hands are working simultaneously
\item Enable new users to join, so that the approval of additional users allows them
to easily engage with your application, without disrupting other users already
present.
\item Be able to continue with fewer users, allowing one user to leave without disrupting all others’ experience.
\end{itemize}
I believe them fitting because in the social context of watching a movie the, the experience would come alive, when people are sitting and discussing their likes, and dislikes.
This could, of course be the case in a chat-room setting such as Slack, as well.
%----------------------------------------------------------------------------------------
%	CHAPTER 3 Interactive System Design
%----------------------------------------------------------------------------------------

\chapterimage{head3.png}
\chapter{Interactive System: Design}
\begin{figure}[]
  \centering
   \includegraphics[width=0.77\textwidth]{system_flow.png}
  \caption{System Flow for Filmchat}
  \label{fig:system_flow}
\end{figure}
•	Sketches
•	Design rationale for the interface
•	Cost/benefit discussion of selected interaction techniques

>>>>

\chapter{Project Description}
\section{Vision}
Imagine the following scenario.You, and one or more friends, or maybe a romantic partner, are sitting in the sofa in front of the TV. You are having a movie night, but you are not quite sure what you should see. While you sit and discuss your likes, and dislikes, there is a microphone hidden in the corner. The listens to what you are saying, and it is sending it to an Interactive System. It understands, who is speaking, who is liking a movie, and who is not liking a movie. It also has, from earlier experience, knowledge of what you and maybe the ones you are with have seen, and liked. It also knows what you did not like.

@@

\chapter{Interactive System: Description}
There are three parts implemented in this system
The first part listens to a given channel on Slack, using the outgoing web hook\cite{SlackOutgoingSlack}.This is the TextBlob Botlisener.Then there is the component that listens to a post message and tries to find a movie from that message. This is the Omdbsearcher.
The third part is the Speech Regognizer which is heavily based on the Csharp example from Googles Speech API \cite{GoogleCloudPlatformSpeechPlatform} and listens to the microphone. It then tries to search for the terms in the recognized speech and if it finds a movie within it it posts it to the same Slack channel.

\section{TextBlob Botlistener}
A Python web service that uses Textblob\cite{TextBlobTutorial:Documentation} as a way of getting noun phrase, and sentiment from the text it is provided. It gets input from the designated slack channel, using the outgoing web hook \cite{SlackOutgoingSlack}. The TextBlob Botlistener listens to port 8080 by default.

\section{Speech Recognizer}
The Speech recognizer, is based on the Google Speech API \cite{GoogleCloudPlatformSpeechPlatform} and is programmed in Csharp. The code is mostly just adapted to post to a web interface, in addition to printing to the console / cli. The Speech Recognizer listens to the detected microphone on the computer by default. It keeps a python dictionary of the users, and their, movie and their most recent sentiment score in memory.

\section{Omdbsearcher}
The Omdbsearcher is based on the Open Movie Data base API.\cite{OMDbDatabase}. When it gets text it will try to search for this text on the OMDB Api and return the JSON formatted result if it finds something, or return a negative result if it does not find anything. The web service listens to port 3000 by default.

\newpage
\section{Architecture}
\begin{figure}[]
  \centering
   \includegraphics[width=0.77\textwidth]{system_flow.png}
  \caption{System Flow for Filmchat}
  \label{fig:system_flow}
\end{figure}
The thought of using both of these ways of integrating, was to be able to understand natural language surrounding how people talk and chat about movies, and then later on have the different parts use the same components. This is also why I opted for a modular approach building small components, that I could add to on a later point, and that was easy to test using Postman.

\section{Description of the vision}
The vision of the project, not the actual implementation sadly, aimed to follow the design guidelines give in the chapter about Social Natural User Interfaces \(NUI\) that Wigdor and Wixon talks about in their Brave NUI World book. \cite{WigdorBraveWorld}

Some of the ones I believe fitting to Filmchat are:
\begin{itemize}
\item Create an experience that comes alive with several users, so that the experience
is more fun or efficient when many hands are working simultaneously
\item Enable new users to join, so that the approval of additional users allows them
to easily engage with your application, without disrupting other users already
present.
\item Be able to continue with fewer users, allowing one user to leave without disrupting all others’ experience.
\end{itemize}
I believe them fitting because in the social context of watching a movie the, the experience would come alive, when people are sitting and discussing their likes, and dislikes.
This could, of course be the case in a chat-room setting such as Slack, as well. In Fig\ref{fig:system_flow} the modular approach can be seen, and building more components, or hooking into third party API's could easily be done. 
%----------------------------------------------------------------------------------------
% CHAPTER 3 Interactive System Design
%----------------------------------------------------------------------------------------

\chapterimage{head3.png}
\chapter{Interactive System: Design}
\section{System Flow}
The system has three main user inputs \(see Fig\ref{fig:system_flow}\) of which two of them are implemented. They are the Speech recognition, and the Chat. The Chat in the implementation listens to a Slack channel using the outgoing web hook \cite{SlackOutgoingSlack}. It then forwards to the sentiment analysis to extract sentiment and noun phrase \cite{WikipediaNounPhrase} this could have been forwarded to other more advanced third party Natural Language Processors\cite{Wikipedia2017NaturalProcessing} such as Wit.AI\cite{Wit.aiWit.ai} and API.AI\cite{API.AIConversationalAPI.AI}. But I decided to use a light weight Python based for faster development, and easier debugging.

The last input, would have used the same modules, but would have gotten their input from a chat room. The difference would have been the more asynchronous behavior of that kind of interaction, but sentiments and information could have been harvested in much the same way.
\section{Design rationale}
